---
title: "IBCF.MTME"
author: "Francisco Javier Luna-Vázquez"
date: "`r format(Sys.Date())`"
output: github_document
---

Item Based Collaborative Filterign For Multi-trait and Multi-environment Data in R.

## Instructions for proper implementation

### Installation

To complete installation of dev version of IBCF.MTME from GitHub, you must have previously installed the devtools package.

```{r installation, eval = FALSE}
install.packages('devtools')
devtools::install_github('frahik/IBCF.MTME')
```

### Quick use 

#### Load data

```{r loadData}
rm(list = ls())
library(IBCF.MTME)
data('Wheat_IBCF')

head(Wheat_IBCF)
```

```{r loadYearData}
data('Year_IBCF')

head(Year_IBCF)
```

### Cross-validation IBCF

```{r CVModel}
CrossV <- CV.RandomPart(Wheat_IBCF, NPartitions = 10, PTesting = 0.25, Set_seed = 123)

pm <- IBCF(CrossV)
summary(pm)

par(mai = c(2, 1, 1, 1))
plot(pm, select = 'Pearson')
plot(pm, select = 'MSEP')
```

### IBCF.Years Function
```{r Years}
data('Year_IBCF')
DataSet <- getMatrixForm(Year_IBCF, withYears = T)

pm4 <- IBCF.Years(DataSet , Years.testing = c('2015', '2016'), Traits.testing = c('T5', 'T6'))
summary(pm4)

barplot(pm4, select = 'Pearson')
barplot(pm4, select = 'MSEP')
```

### Transform TidyData to Matrix and rollback

```{r MatrixAndTidy}
data('Wheat_IBCF')

M <- getMatrixForm(Wheat_IBCF)
dim(M)

Tidy <- getTidyForm(M)
dim(Tidy)
```


## Citation

How to cite the package...

## Authors

Francisco Javier Luna-Vázquez (Author, Maintainer)

Osval Antonio Montesinos-López (Author)
